---
title: "R-eproducibility Assignment"
output: html_document
---
Project Info:
# January 24, 2022
# https://github.com/alanamcphail/BIOL432Assignement3AlanaMcPhail.git

## Setting wokring directory
```{r}
setwd("/Users/alanamcphail/BIOL432Assignement3AlanaMcPhail/InputData")
```

## Loading packages
```{r}
library(dplyr)
```
## Loading data 
```{r}
fallo <- read.csv("FallopiaData.csv")
```

## Removing rows with 'Total' biomass < 60
```{r}
Fallo1 <- subset(fallo, Total>60 | Total==60)
```

## Reordering the columns and only keeping these columns
```{r}
Fallo2 <- select(Fallo1, Total, Taxon, Scenario, Nutrients)
```

## Making a new column which converts Total into grams and replaces total 
```{r}
Fallo3 <- mutate(Fallo2, TotalG = Total/1000)
Fallo4 <- select(Fallo3, TotalG, Taxon, Scenario, Nutrients)
```

## Making custom funciton
```{r}
myFunction <- function(var1, var2){
  if(var2 == "Average"){
    X <- mean(var1)
    print(paste(X))
  } else if(var2 == "Sum") {
    X <- sum(var1)
    print(paste(X))
  } else if(var2 == "Observations"){
    X <- length(unique(var1))
    print(paste(X))
  } else{
      print("Error")
    }
  }
```


## Testing funcition
```{r}
myFunction(var1 = Fallo1$PotNum, var2="Average")
```

## Using function to count number of observations in the "Taxon" column 
```{r}
myFunction(var1 = Fallo1$Taxon, var2 ="Observations")
```


## Creating subsets of the two nutrient concentrations
```{r}
low <- subset(Fallo4, Nutrients == "low")
high <- subset(Fallo4, Nutrients == "high")
```

## Using myFunction to find TotalG mean of the low nutrients concentration
```{r}
myFunction(var1 = low$TotalG, var2 = "Average")
```

## Using myFunction to find TotalG mean for the high nutrients concentration
```{r}
myFunction(var1 = high$TotalG, var2 = "Average")
```

```{r}
write.csv(Fallo4, "WrangledData.csv")
```







